---
title: "Assignment 4"
author:
- familyname: Sarkar
  othernames: Arpan
  address: India
  email: "asar0035@student.monash.edu"
  correspondingauthor: true
  qualifications: Masters In Business Analytics (Student) 
- familyname: Cui
  othernames: Xinyi
  address: China
  email: "xcui0006@student.monash.edu"
  correspondingauthor: true
  qualifications: Masters In Business Analytics (Student) 
- familyname: Liu
  othernames: Yalong
  address: China
  email: "yliu0406@student.monash.edu"
  correspondingauthor: true
  qualifications:  Masters In Business Analytics (Student)
department: Business Growth Hackers\newline Arpan Sarkar &\newline Xinyi Cui &\newline Yalong Liu
organization: World Bank Group
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r loading-packages}
library(tidyverse)
library(plotly)
```

# How different states and territory RBT results different from each other?

## Introduction

```{r loading-data, message=FALSE}
alcohol <- read.csv("data/bitre_enforcement_data-rbt.csv")
```

```{r Overview-of-postiveRBT-by-state, fig.height=8, fig.width=12}
p1<- ggplot(alcohol, aes(x = Year, y = Positive.RBT, group = State))+
  geom_line(aes(color=State))+
  geom_point(aes(color=State)) +
  ggtitle("Overview of positive RBT") +
  theme_bw()
  
ggplotly(p1)
```

The graph above presents the positive RBT test result from 2008 to 2019 for each state in Australia. 
Some interesting findings from the graph:

- The highest positive RBT result was in 2010 **Queensland** of 33638 positive results. 

- Queensland and New South Wales are the two states having the highest number of positive RBT.

- In general, there is a decreasing trend for positive RBT over the years for all states and territories

- Tasmania and Australian Capital Territory remained low positive RBT from 2008 to 2019.